The Anatomy of a Temporal Summarization System

### 2015-05-29 methods.tex
spellinggit add acl2015.tex conclusion.tex dataset.tex experiments.tex introduction.tex methods.tex relatedwork.tex results.tex rouge_cum.tex nuggets-metrics-eps-converted-to.pdf rouge-time-eps-converted-to.pdf !

\label{sec:methods}
%In order to evaluate an update summarization system, we adopt the simulation-based approach used in the TREC Temporal Summarization (TS) Track.  We provide a brief overview of the problem.  Details on the formulation can be found in the track overview paper \cite{aslam2013trec}.

Our update summarization system takes as input 
\begin{enumerate*}[label=\itshape\alph*\upshape)]
  \item a short query defining the event to be tracked (e.g. `Hurricane Sandy'), 
  \item an event category defining the type of event to be tracked (e.g. `hurricane'), 
  \item a stream of time-stamped documents %, $(\doc_0, \doc_1,\ldots,\doc_T)$,
  presented in temporal order, and \item an evaluation time period of interest.
    %  $(\stime,\etime)$.  
\end{enumerate*} 
While processing documents
throughout the time period of interest, the system outputs sentences
from these documents likely to be useful to the query issuer.  We refer
to these selected sentences as \emph{updates}.

In order to measure the usefulness of a system's updates, we consider
the degree to which the system output reflects the different
aspects of an event.  Events are often composed of a variety of sub-events.  
For example, the Hurricane Sandy
event includes sub-events related to the storm making landfall,
the ensuing flooding, the many transportation issues, among many
others.  An ideal system would update the user about each of these
sub-events as they occur. %, with low latency.  
%In order to use
%language consistent with previous literature, 
We refer to these
sub-events as the \emph{nuggets} associated with an event.  A nugget is
defined as a fine-grained atomic sub-event associated with an event.  
%An example nugget for Hurricane Sandy might be ``Sandy on course for the Jersey Shore.''
We present 2 example nuggets associated with the Hurricane
Sandy event 
in Figure \ref{fig:nuggets}. 
Note that each event has anywhere from 50 to
several hundred nuggets in total in our gold dataset.
%Note that each event has anywhere from 50 to
%several hundred nuggets in total.
We describe how these 
nuggets are found in Section \ref{sec:data}.

@@

Throughout our treatment of our algorithm, the \emph{salience} 
of an update captures the degree to which it reflects an 
event's nuggets.  Assuming that we have a text representation 
for each of our nuggets, the salience of an update $u$  with respect to a set of nuggets $N$ is
defined as,
\begin{align}
\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \label{eq:salience}
\end{align}
where $\operatorname{sim}(\cdot)$ is the semantic similarity such as
the cosine similarity of latent vectors associated with the update and 
nugget text \cite{guo2012simple}.

@@

Our system architecture follows a simple pipeline design where each
stage provides an additional level of processing or filtering of the input
sentences.
We begin with an empty update summary $U$.
At each hour we receive a new batch of sentences $b_t$ from the stream
of event relevant documents
and perform the following actions:
\begin{enumerate}[nosep]
  \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences in $b_t$ by combining 
      clustering with 
      salience predictions (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars 
      to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}
The resultant list of updates $U$ is our summary of the event.

@@

%include feature table
%\input{feature_table.tex}

\subsubsection{Features}
\label{sec:features}
We want our model to be predictive of sentence salience across different event instances so we avoid lexical features.  Instead, we extract features such as language model scores, geographic relevance, and temporal relevance from each sentence.

@@

The second model is estimated from text specific to our event types.  
For each event type we create a corpus of related documents using pages
and subcategories listed under a related Wikipedia category.
For example, the language model for event type `earthquake' is estimated 
from Wikipedia pages under the category \emph{Category:Earthquakes}.  
%\fdcomment{stress here that this technique can be applied in situations beyond crisis; any situation where the
%expected summary is similar to some previously seen target or some side information.}
These models are intended to detect sentences similar to those appearing in 
summaries of other events in the same category 
(e.g. most earthquake summaries are likely to include higher probability for 
ngrams including the token `magnitude'). While we focus our system on the 
language of news and disaster, we emphasize that the use of language modeling 
can be an effective feature for multi-document summarization for other 
domains that have related text corpora.

@@

%KM - Note: Someplace the exact list of event types should appear. Probably not
%here.
%KM - I note you have it in a later section but it is labeled as data you use
%to train language models and semantic similarity. I think it would be good to
%have up front in definition of task.

\textbf{Geographic Relevance Features}
%\fdcomment{need introduction here.  what are geographic features?}
The disasters in our corpus are all phenomena that
affect some part of the world. 
Where possible, we would like to capture a sentence's proximity to the event,
i.e. when a sentence references a location, it should be close to the 
area of the disaster.

There are two challenges to using geographic features. First we do not 
know where the event is, and second, most sentences do not contain references
to a location.
We address the first issue by extracting all locations from 
documents relevant to the event at the
current hour and looking up their latitude and 
longitude using a publicly available geolocation service. 
%\fdcomment{is this all documents in the bucket or the filtered set?  is it a biased sample?}
Since the documents that are at least somewhat relevant to the event,
we assume in aggregate the locations should give us a rough area of interest.
The locations are clustered %(using affinity propagation and uniform salience)
%\fdcomment{affinity propagation undefined}
and we treat the resulting cluster centers
as the event locations for the current time.

%\ckcomment{(Paragraphs in blue should replace last two paragraphs in geo relevance section)\\
The second issue arises from the fact that the majority of sentences in our 
data do not contain explict references to locations, i.e. a sequence of tokens
tagged as location named entities.   
Our intuition is that geographic relevance is important in the disaster
domain, and we would like to take advantage of the sentences that do have 
location information present. To make up for this imbalance, we  
%Extracting features for just these sentences
%would leave 
% Last sentence is unclear
%Assigning a null or default value to sentences without explicit location is 
%not a viable option as 
%the imbalance of null/default values would make it difficult for the model
%to learn meaningful weights for these features.
% also unclear
instead compute an overall location for the document and derive 
geographic features based on the document's proximity to the event in 
question.
These features are assigned to all sentences in the document.\\\\
Our method of computing document-level geographic relevance features is as 
follows.
Using the locations in each document, we compute the median distance to the 
nearest event location. Because document position is a good indicator 
of importance we also compute the distance of the first mentioned
location to the nearest event location. All sentences in the document take
as features these two distance calculations.
Because some events can move, we also
compute these distances to event locations from the previous hour.
%}

%To address the second issue, 
%we compute features for the document as a whole and all
%sentences from that document receive the same feature value.

%Using the locations in each document, we compute the median distance to the 
%nearest event location. Because document position is a good indicator 
%of importance we also compute the distance of the first mentioned
%location to the nearest event location. All sentences in the document take
%as features these two distance calculations.
%Because some events can move, we also
%compute these distances to event locations from the previous hour.

\textbf{Temporal Relevance Features}
%\fdcomment{motivate burstiness; explain what it is before using the expression.}
As we track events over time, it is likely that the coverage of the event 
may die down, only to spike back up when there is a breaking development.
%Alternatively, words that were salient initially may become background context,
%and over time lose their importance.
Identifying terms that are ``bursty,'' i.e. suddenly peaking in usage,
can help to locate novel sentences that are part of the most recent reportage
and have yet to fall into the background.

We compute the IDF for each hour in our data stream. 
For each sentence, the average TFIDF for the current hour $t$ is taken as a 
feature. Additionally, we use the difference in average TFIDF from time $t$
to $t-i$ for $i = \{1, \ldots, 24\}$ to measure how the TFIDF scores for the 
sentence have changed over the last 24 hours, i.e. we keep the sentence
term frequencies fixed and compute the difference in IDF. Large changes
in IDF value indicate the sentence contains bursty terms.
%\fdcomment{unclear.  is it just changing the IDF part of the 
%items in the average?}
We also use the time (in hours) since the event started as a feature.
%difference 
%Using these IDF 
%calculations, the avg TFIDF is calculated for
%Let $D_t$ be the set of web pages at time $t$ and let $s = \{w_1,\ldots,w_n\}$ be a sentence from a page $d \in D_t$.  We calculate the 1-hour burstiness of sentence $s$ from document $d$ at hour $t$  as 
%\begin{align*}
%\operatorname{b}_1(s,d,t) = \frac{1}{|s|} \sum_{w \in s} \Bigg( &
%\operatorname{tf-idf}_t(w,d)  \\ & \left. - \frac{\sum_{d^\prime \in D_{t-1}:
%w \in d^\prime } \operatorname{tf-idf}_{t-1}(w,d^\prime)}{|\{d^\prime \in
%D_{t-1}: w \in d^\prime\}|} \right) \end{align*}

%where \begin{align*} \operatorname{tf-idf}_t(w,d) =&
%\log\left(1+\sum_{w^\prime \in d}1\{w=w^\prime\}  \right)\\ & \times
%\log\left(\frac{|D_t|}{1 + \sum_{d^\prime \in D_t}1\{w \in d^\prime\}}\right).
%\end{align*}

%[\textrm{Simpler explanation goes here}]
% 1\{w = w^\prime} %- \operatorname{avg-tf-idf}_{t_{i-1}}(w).
%\end{align*}

%We similarly find the sentence's 5-hour burstiness.  In addition to burstiness, we also include the sentence's average tf-idf and

% Formally, let $p(f)$ be a distribution over functions where $f$ is any mapping
% of an input space $\mathcal{X}$ to the reals,
%
% $$f: \mathcal{X} \rightarrow \mathcal{R}.$$
% Let the random variable $\mathbf{f} = (f(x_1),\ldots,f(x_n) )$ be
%  an $n$-dimensional vector whose elements are evaluations of the function $f$
% at points $x_i \in \mathcal{X}$.
% We say $p(f)$ is a Gaussian process if for any finite subset
% $\{x_1,\ldots,x_n\} \subset \mathcal{X}$, the marginal distribution over
% that finite subset $p(\mathbf{f})$ has a multivariate Gaussian distribution.
% A GP is parameterized by a mean function $\mu(\mathbf{x})$ and a
% covariance function $K(x,x^\prime)$. Generally, the mean function is simply
% set to 0, leaving the distribution to be completely characterized by the
% kernel function on the data.
%
% In the regression setting, we typically have a response variable $y$ that
% is the sum of our model prediction  and
% some Gaussian noise, i.e. $y = f(x) + \epsilon$ with
% $\epsilon \sim \mathcal{N}(0, \sigma^2)$. When
% $f \sim \operatorname{GP}(\mathbf{0}, \mathbf{K})$, the
% two distributions
% of principal interest are the marginal likelihood
% $p(\mathbf{y}|\mathbf{X}) =
% \mathcal{N}(\mathbf{0},\mathbf{K} + \sigma^2\mathbf{I})$ and the predictive
% distribution,
%
% $$p(\mathbf{y_*}|\mathbf{x_*},\mathbf{X},\mathbf{y}) =
% \mathcal{N}(\boldsymbol{\mu}_*, \boldsymbol{\sigma}^2_*) $$
%
% where $\mathbf{x_*}$ is a new or unseen input, $\mathbf{y_*}$ our predicted
% response, and
% \begin{align*}
% \boldsymbol{\mu}_* & = \mathbf{K_*}(\mathbf{K} + \sigma^2\mathbf{I})^{-1}\mathbf{y} \\
% \boldsymbol{\sigma}^2_* &
% = \mathbf{K}_{**} - \mathbf{K}_*(\mathbf{K} + \sigma^2\mathbf{I})^{-1}
% \mathbf{K}_*^T + \sigma^2\\
% \end{align*}.
%
% Here $\mathbf{K}_* = K(\mathbf{x}_*, \mathbf{X})$, and
% $\mathbf{K}_{**} = K(\mathbf{x}_*, \mathbf{x}_*)$.
%
%

\subsubsection{Model}
%\ckcomment{(replace section with this)\\
Given our feature representation of the input sentences, we need only target 
salience values for model learning. 
For each event in our training data, we sample a set of sentences and  each 
sentence's salience is computed according to Equation \ref{eq:salience}.
This results in a training set of sentences, their feature representations,
and their target salience values to predict.

%Given the feature representation/salience pairs, we can use
%any regression technique to predict salience.
We opt to use a Gaussian process (GP) regression model
\cite{rasmussen:gaussian-process-book} with a Radial Basis Function (RBF) 
kernel for the salience prediction task.  
Our features fall naturally into five groups and we use a separate RBF kernel
for each, using the sum of each feature group RBF kernel as the final input
to the GP model.
%}

%At run-time
%our summarization system
%does not have access to event nuggets to compute sentence salience. 
%However, we can use the nuggets
%in our training data to model salience as a function of our features.
%Such a model generalizes to new events.
%For each event in our training data, we sample a set of sentences and  each 
%sentence's salience is computed according to Equation \ref{eq:salience}.
%This results in a training set of sentences and the target values 
%(their salience) to predict.
%
%Given a feature representation for the sentences, we can use
%any regression technique to predict salience.
%We opt to use a Gaussian process (GP) regression model
%\cite{rasmussen:gaussian-process-book} with a Radial Basis Function (RBF) 
%kernel.  
%Our features fall naturally into five groups and we use a separate RBF kernel
%for each, using the sum of each feature group RBF kernel as the final input
%to the GP model.

%GP regressors are a
%class of data-driven, non-parametric model generalizing the multi-variate
%Gaussian to the infinite dimensional setting.

%When evaluating
%In order to fit a regression model, the sentences are represented as feature
%vectors (described in Section~\ref{sec:features}).
%GP's are general
%and are state of the art for many regression tasks.  
%GP's are non-parametric and rely on a covariance matrix $\kernelMatrix$, measuring the similarity between pairs of instances, in our 
%case sentences.  In our experiments, we used a radial basis 
%function (RBF) kernel.

@@

Once we have predicted the salience for a batch of sentences, we must
now select a set of update candidates, i.e. sentences that are both salient
and representative of the current batch.
To accomplish this, we combine the output of our 
salience prediction model with the affinity
propagation algorithm.
%to identify a set of exemplar sentences 
%for each input batch. 
Affinity propagation (AP) is a clustering algorithm
that identifies a subset of datapoints as exemplars and forms clusters
by assigning the remaining points to one of the exemplars 
\cite{frey2007clustering}. AP attempts to 
maximize the net similarity objective 
\[ \mathcal{S} = \sum_{i : i \neq e_i}^n \operatorname{sim}(i,e_i) 
+ \sum_{i : i = e_i}^n \operatorname{salience}(e_i)  \]
where $e_i$ is the exemplar of the $i$-th data point, and functions
$\operatorname{sim}$ and $\operatorname{salience}$ express the pairwise 
similarity
of data points and our predicted \textit{apriori} preference of a data point to be an exemplar
respectively. 
AP differs from other $k$-centers algorithms in that it simultaneously 
considers all data points as exemplars, making it less prone to finding
local optima as a result of poor initialization. Furthermore, the 
second term in $\mathcal{S}$ incorporates the individual importance of 
data points as candidate exemplars; most other clustering algorithms only make
use of the first term, i.e. the pairwise similarities between data points.

%There are very 
%few restrictions on the nature of the similarities and preferences
%other than that they be real-valued.

@@

%In our summarization system we use the output of our salience model as 
%the preferences, i.e.
%$\operatorname{salience}(s) = \operatorname{pref}(s)$; for the similarity 
%function we use semantic similarity. 
Recall that $\operatorname{salience}(s)$
is a prediction of the semantic similarity of $s$ to information about the 
event be summarized, i.e. the set of event nuggets.
Intuitively, when maximizing objective function $\mathcal{S}$, AP must balance
between best representing the input data and representing the most salient
input. Additionally, when the level of input is high but the salience
predictions are low, the preference term will guide AP toward a solution
with fewer clusters; \textit{vice-versa} when input is very salient on average but
the volume of input is low. The adaptive nature of our model differentiates
our method from most other update summarization systems.

@@

 Next,
to prevent adding updates that are redundant with previous output updates, 
we filter out exemplars
that are too similar to previous updates.
The exemplars are examined
sequencially in order of decreasing salience and  a similarity threshold 
is applied, where the exemplar is ignored if its
maximum semantic similarity to any previous updates in the summary is
greater than $\lambda_{sim}$.

>>>>

\label{sec:methods}

Our update summarization system takes as input 
\begin{enumerate*}[label=\itshape\alph*\upshape)]
  \item a short query defining the event to be tracked 
  (e.g. `Hurricane Sandy'), 
  \item an event category defining the type of event to be tracked 
  (e.g. `hurricane'), 
  \item a stream of time-stamped documents presented in temporal order, 
  and \item an evaluation time period of interest.
\end{enumerate*} 
While processing documents throughout the time period of interest, the system 
outputs sentences from these documents likely to be useful to the query 
issuer.  We refer to these selected sentences as \emph{updates}.

In order to measure the usefulness of a system's updates, we consider the 
degree to which the system output reflects the different aspects of an event.
Events are often composed of a variety of sub-events.  For example, the 
Hurricane Sandy event includes sub-events related to the storm making 
landfall, the ensuing flooding, the many transportation issues, among many
others.  An ideal system would update the user about each of these
sub-events as they occur. We refer to these sub-events as the \emph{nuggets} 
associated with an event.  A nugget is defined as a fine-grained atomic 
sub-event associated with an event.  We present 2 example nuggets associated 
with the Hurricane Sandy event in Figure \ref{fig:nuggets}. Each event has 
anywhere from 50 to several hundred nuggets in total in our gold dataset.
We describe how these nuggets are found in Section \ref{sec:data}.

@@

Throughout our treatment of our algorithm, the \emph{salience} of an update 
captures the degree to which it reflects an event's unobserved nuggets.  
Assuming that we have a text representation for each of our nuggets, the 
salience of an update $u$  with respect to a set of nuggets $N$ is defined as,
\begin{align}
\operatorname{salience}(u) = \operatorname{max}_{n \in N} 
\operatorname{sim}(u, n) \label{eq:salience}
\end{align}
where $\operatorname{sim}(\cdot)$ is the semantic similarity such as the 
cosine similarity of latent vectors associated with the update and nugget 
text \cite{guo2012simple}.

@@

Our system architecture follows a simple pipeline design where each stage 
provides an additional level of processing or filtering of the input 
sentences. We begin with an empty update summary $U$. At each hour we receive 
a new batch of sentences $b_t$ from the stream of event relevant documents
and perform the following actions:
\begin{enumerate}
  \item predict the salience of sentences in $b_t$ (Section~\ref{sec:salpred}),
  \item select a set of exemplar sentences in $b_t$ by combining 
      clustering with 
      salience predictions (Section~\ref{sec:exsel}),
  \item add the most novel and salient exemplars 
      to $U$ (Section~\ref{sec:upsel}).
\end{enumerate}
The resultant list of updates $U$ is our summary of the event.

@@

\subsubsection{Features}
\label{sec:features}

We want our model to be predictive of sentence salience across different event instances so we avoid event-specific lexical features.  Instead, we extract features such as language model scores, geographic relevance, and temporal relevance from each sentence.

@@

The second model is estimated from text specific to our event types.  For each
event type we create a corpus of related documents using pages and 
subcategories listed under a related Wikipedia category. For example, the 
language model for event type `earthquake' is estimated from Wikipedia pages 
under the category \emph{Category:Earthquakes}.  These models are intended to 
detect sentences similar to those appearing in summaries of other events in 
the same category (e.g. most earthquake summaries are likely to include 
higher probability for ngrams including the token `magnitude'). While we focus
our system on the language of news and disaster, we emphasize that the use of 
language modeling can be an effective feature for multi-document summarization
for other domains that have related text corpora.

@@

\textbf{Geographic Relevance Features}
The disasters in our corpus are all phenomena that affect some part of the 
world. Where possible, we would like to capture a sentence's proximity to the 
event, i.e. when a sentence references a location, it should be close to the 
area of the disaster.

There are two challenges to using geographic features. First, we do not know 
where the event is, and second, most sentences do not contain references to a 
location. We address the first issue by extracting all locations from 
documents relevant to the event at the current hour and looking up their 
latitude and longitude using a publicly available geo-location service. 
Since the documents that are at least somewhat relevant to the event, we 
assume in aggregate the locations should give us a rough area of interest.
The locations are clustered and we treat the resulting cluster centers as the 
event locations for the current time.

The second issue arises from the fact that the majority of sentences in our 
data do not contain explicit references to locations, i.e. a sequence of 
tokens tagged as location named entities. Our intuition is that geographic 
relevance is important in the disaster domain, and we would like to take 
advantage of the sentences that do have location information present. To make 
up for this imbalance, we instead compute an overall location for the document
and derive geographic features based on the document's proximity to the event
in question. These features are assigned to all sentences in the document.

Our method of computing document-level geographic relevance features is as 
follows. Using the locations in each document, we compute the median distance 
to the nearest event location. Because document position is a good indicator 
of importance we also compute the distance of the first mentioned location to 
the nearest event location. All sentences in the document take as features 
these two distance calculations. Because some events can move, we also compute
these distances to event locations from the previous hour.

\textbf{Temporal Relevance Features}
As we track events over time, it is likely that the coverage of the event 
may die down, only to spike back up when there is a breaking development.
Identifying terms that are ``bursty,'' i.e. suddenly peaking in usage,
can help to locate novel sentences that are part of the most recent reportage
and have yet to fall into the background.

We compute the IDF for each hour in our data stream. For each sentence, the 
average TF*IDF for the current hour $t$ is taken as a feature. Additionally, 
we use the difference in average TF*IDF from time $t$ to $t-i$ for 
$i = \{1, \ldots, 24\}$ to measure how the TF*IDF scores for the sentence have
changed over the last 24 hours, i.e. we keep the sentence term frequencies 
fixed and compute the difference in IDF. Large changes in IDF value indicate 
the sentence contains bursty terms.
We also use the time (in hours) since the event started as a feature.

\subsubsection{Model}

Given our feature representation of the input sentences, we need only target 
salience values for model learning. For each event in our training data, we 
sample a set of sentences and  each sentence's salience is computed according 
to Equation \ref{eq:salience}. This results in a training set of sentences, 
their feature representations, and their target salience values to predict.

We opt to use a Gaussian process (GP) regression model
\cite{rasmussen:gaussian-process-book} with a Radial Basis Function (RBF) 
kernel for the salience prediction task. Our features fall naturally into 
five groups and we use a separate RBF kernel for each, using the sum of each 
feature group RBF kernel as the final input to the GP model.

@@

Once we have predicted the salience for a batch of sentences, we must
now select a set of update candidates, i.e. sentences that are both salient
and representative of the current batch. To accomplish this, we combine the 
output of our salience prediction model with the affinity propagation 
algorithm.
Affinity propagation (AP) is a clustering algorithm
that identifies a subset of data points as exemplars and forms clusters
by assigning the remaining points to one of the exemplars 
\cite{frey2007clustering}. AP attempts to maximize the net similarity 
objective 
\[ \mathcal{S} = \sum_{i : i \neq e_i}^n \operatorname{sim}(i,e_i) 
+ \sum_{i : i = e_i}^n \operatorname{salience}(e_i)  \]
where $e_i$ is the exemplar of the $i$-th data point, and functions
$\operatorname{sim}$ and $\operatorname{salience}$ express the pairwise 
similarity of data points and our predicted \textit{apriori} preference of a 
data point to be an exemplar respectively. 
AP differs from other $k$-centers algorithms in that it simultaneously 
considers all data points as exemplars, making it less prone to finding local 
optima as a result of poor initialization. Furthermore, the second term in 
$\mathcal{S}$ incorporates the individual importance of data points as 
candidate exemplars; most other clustering algorithms only make use of the 
first term, i.e. the pairwise similarities between data points.

@@

Recall that $\operatorname{salience}(s)$ is a prediction of the semantic 
similarity of $s$ to information about the event be summarized, i.e. the set 
of event nuggets. Intuitively, when maximizing objective function 
$\mathcal{S}$, AP must balance between best representing the input data and 
representing the most salient input. Additionally, when the level of input is 
high but the salience predictions are low, the preference term will guide AP 
toward a solution with fewer clusters; \textit{vice-versa} when input is very 
salient on average but the volume of input is low. The adaptive nature of our 
model differentiates our method from most other update summarization systems.

@@

Next, to prevent adding updates that are redundant with previous output 
updates, we filter out exemplars that are too similar to previous updates.
The exemplars are examined sequentially in order of decreasing salience and  a similarity threshold is applied, where the exemplar is ignored if its maximum 
semantic similarity to any previous updates in the summary is greater than 
$\lambda_{sim}$.

### 2015-05-29 relatedwork.tex
Addressed comments. Fixed margins/sizings. Added authors.
spellinggit add acl2015.tex conclusion.tex dataset.tex experiments.tex introduction.tex methods.tex relatedwork.tex results.tex rouge_cum.tex nuggets-metrics-eps-converted-to.pdf rouge-time-eps-converted-to.pdf !

A principal concern in extractive multi-document summarization is the
selection of salient sentences for inclusion in summary output
\cite{nenkova2012survey}. 
%We conceptualize 
Existing approaches generally fall into  %falling into
one of three categories, each with specific tradeoffs with respect to update 
summarization.

@@

The second category, predictive approaches,
includes ranking and classification based methods.
Sentences have been ranked by the average word probability, average tf-idf
score, and the number of topically related words (topic-signatures in the
summarization literature)
\cite{nenkova2005impact,hovy1998automated,lin2000automated}. The first two
statistics are easily computable from the input sentences, while the third
only requires an additional, generic background corpus.  
In classification based methods, model features are
usually derived from human generated summaries, and are non-lexical in nature
(e.g., sentence starting position, number of topic-signatures, number of
unique words). Seminal work in this area has employed naive
Bayes and logistic regression classifiers to identify sentences for summary
inclusion \cite{kupiec1995trainable,conroy2001using}. 
While these methods are less dependent on redundancy, the expressiveness of
their features is limited. Our model expands on these basic features to 
account for geographic, temporal, and language model features.

The last category includes probabilistic \cite{haghighi2009exploring}, 
information theoritic, and set cover \cite{lin2011class}
approaches. While these methods are  focused on producing diverse
summaries, they are difficult to adapt to the streaming setting, where 
we do not necessarily have a fixed summary length and the corpus to be
summarized contains many irrelevent sentences, i.e. there are large
portions of the corpora that we specificly want to avoid.

% This has often been approached as a ranking
%problem.
%We broadly conceptualize this decision as either an intrinsic or extrinsic
%sentence evaluation process. Intrinsic approaches evaluate sentences
%individually, possibly by predicting the impact on summary quality using
%sentece level features. 
%Sentences have been ranked by the average word probability, average tf-idf
%score, and the number of topically related words (topic-signatures in the
%summarization literature)
%\cite{nenkova2005impact,hovy1998automated,lin2000automated}. The first two
%statistics are easily computable from the input sentences, while the third
%only requires an additional, generic background corpus.  Another ranking
%approach, centroid summarization, involves creating an average bag of words
%(BOW) vector, the centroid, from the input sentences and ranking sentences by
%their similarity to the centroid \cite{radev2004centroid}.  Graph
%\cite{erkan2004lexrank} and clustering
%\cite{hatzivassiloglou2001simfinder,mckeown1999towards,siddharthan2004syntactic}
%based approaches, on the other hand, make use of pair-wise similarity
%comparisons amongst input sentences.  In these models, salient sentences are
%more central to the input or cluster, respectively.

%identify salient regions of the input space while simultaneously coping with
%redundancy.  Graph-based algorithms have been used to rank sentences
%Clustering algorithms, e.g., are commonly used to exploit redundancy in
%input. Input sentences are clustered and summaries are generated by selecting
%the most representative sentence from each cluster.  Graph-based models have
%also been used for summarization.  E.g., the LexRank algorithm treats
%sentences as nodes in a graph, where edges are constructed by way of cosine
%similarity between sentence nodes; edges are either continuosly weighted by
%similarity or discrete, existing only when the similarity is above a
%threshold.  The PageRank algorithm is used on the graph to find the most
%important sentence nodes. In both clustering and graph-based approaches,
%sentence salience is largely determined by the pairwise relations between
%sentences.

%\fdadd{
Several researchers have recognized the importance of summarization during
natural disasters.  \cite{qi:temporal-summarization} developed a system for detecting
novel, relevant, and comprehensive sentences immediately after a natural
disaster.  
%The method uses a model of
%sentence relevance and novelty in order to select appropriate updates.
%Training data for regression targets is automatically generated from
%retrospective Wikipedia data.  The system is evaluated on news documents
%related to 197 natural and human disasters from 2009 to 2011 using variants of
%ROUGE modified to capture novelty, relevance, and comprehensiveness
%\cite{lin2004rouge}.  
\cite{wang:update-summarization} present a clustering-based approach to
efficiently detect important updates during natural disasters.  
The algorithm works by hierarchically
clustering sentences online, allowing the system to output a more expressive
narrative structure than \cite{qi:temporal-summarization}.  
Our system attempts to unify these system's approaches 
(predictive ranking and clustering respectively). 
%The method is evaluated on
%official press releases related to Hurricane Wilma  in 2005 using ROUGE score
%between the system summary and a manually generated target summary. 
%In addition
%to natural disasters, we evaluate our system on a variety of event types 
% such as terrorism and mass shootings (e.g., the 2012
%shooting in Aurora, Col.), accidents
%(e.g., the 2012 Pakistan garment factory fire), and social activism (e.g., the
%Arab spring). The size and scope of the events varies considerably. Hurricane
%Sandy, for example, affected multiple countries over weeks while the
%2012 Aurora shooting was contained to a single location spanning several hours.

%\fdcomment{Glasgow temporal summarization system \cite{mccreadie:temporal-summarization}.}

>>>>

A principal concern in extractive multi-document summarization is the
selection of salient sentences for inclusion in summary output
\cite{nenkova2012survey}. 
Existing approaches generally fall into one of three categories, each with 
specific trade-offs with respect to update summarization.

@@

The second category, predictive approaches, includes ranking and 
classification based methods. Sentences have been ranked by the average word 
probability, average TF*IDF score, and the number of topically related words 
(topic-signatures in the summarization literature)
\cite{nenkova2005impact,hovy1998automated,lin2000automated}. The first two
statistics are easily computable from the input sentences, while the third
only requires an additional, generic background corpus. In classification 
based methods, model features are usually derived from human generated 
summaries, and are non-lexical in nature (e.g., sentence starting position, 
number of topic-signatures, number of unique words). Seminal work in this 
area has employed na\"ive Bayes and logistic regression classifiers to 
identify sentences for summary inclusion 
\cite{kupiec1995trainable,conroy2001using}. 
While these methods are less dependent on redundancy, the expressiveness of
their features is limited. Our model expands on these basic features to 
account for geographic, temporal, and language model features.

The last category includes probabilistic \cite{haghighi2009exploring}, 
information theoretic, and set cover \cite{lin2011class}
approaches. While these methods are  focused on producing diverse
summaries, they are difficult to adapt to the streaming setting, where 
we do not necessarily have a fixed summary length and the corpus to be
summarized contains many irrelevant sentences, i.e. there are large
portions of the corpora that we specifically want to avoid.

Several researchers have recognized the importance of summarization during
natural disasters.  \cite{qi:temporal-summarization} developed a system for 
detecting novel, relevant, and comprehensive sentences immediately after a 
natural disaster.  \cite{wang:update-summarization} present a clustering-based
approach to efficiently detect important updates during natural disasters.  
The algorithm works by hierarchically clustering sentences online, allowing 
the system to output a more expressive narrative structure than 
\cite{qi:temporal-summarization}.  Our system attempts to unify these system's
approaches (predictive ranking and clustering respectively).
